### 2024-03-27 assets/chapter_4/riscatter.tex
:pencil: Update chapter 4

\begin{tikzpicture}[every node/.style={draw,ultra thick},every path/.style={ultra thick},every text node part/.style={align=center}]
	\node at (0,0) [dart,shape border rotate=90,minimum width=1cm] {};
	\node at (5,3.25) [semicircle,shape border rotate=180,minimum width=1.5cm] {};
	\node at (8,0.35) [dart,shape border rotate=270,minimum width=1cm] {};

	\node[draw=none] at (0,-1) {Transmitter};
	\node[draw=none] at (5,4.4375) {Reflect\\Element};
	\node[draw=none] at (8,-1) {Receiver};

	\draw[blue,decorate,decoration={waves,segment length=4mm,radius=2mm}] (1,-0.25) -- (7.375,-0.25);
	\draw[blue,decorate,decoration={waves,segment length=4mm,radius=2mm}] (0.5,0.75) -- (4,3);
	\draw[blue,decorate,decoration={waves,segment length=4mm,radius=2mm}] (6,3.1625) -- (8,1.25);

	\node[draw=none] at (4.625,1) {Modulated};
\end{tikzpicture}

>>>>

\begin{tikzpicture}[every node/.style={draw,ultra thick},every path/.style={ultra thick},every text node part/.style={align=center}]
	\node at (0,0) [circular sector,shape border rotate=90,minimum width=2cm] {};
	\node at (5,3) [circle,minimum size=1.25cm] {};
	\node at (8,0.55) [circular sector,shape border rotate=270,minimum width=2cm] {};

	\node[draw=none] at (0,-1.25) {Primary\\Transmitter};
	\node[draw=none] at (5,4.5) {RIScatter\\Node};
	\node[draw=none] at (8,-1.25) {Co-located\\Receiver};

	\draw[blue,decorate,decoration={waves,segment length=4mm,radius=2mm}] (1,-0.25) -- (7.375,-0.25);
	\draw[blue,decorate,decoration={waves,segment length=4mm,radius=2mm}] (0.5,0.75) -- (4,3);
	\draw[blue,decorate,decoration={waves,segment length=4mm,radius=2mm}] (6,3.1625) -- (8,1.25);
	\draw[green,decorate,decoration={crosses,segment length=8mm,shape size=1.5mm}] (6.29,2.885) -- (8,1.25);

	\node[draw=none] at (3.5,0.75) {Modulated};
	\node[draw=none] at (8,2.76) {Flexible};
\end{tikzpicture}

### 2024-03-27 content/chapter_2.tex
:pencil: Update chapter 4

		\begin{subsubsection}{Diagonal Phase Shift Model}
			A straightforward way to model the \gls{ris} scattering effect is to consider independent scattering elements with purely reactive load impedance \cite{Wu2018}.
			The reflection coefficient of the $n$-th element is thus
			\begin{equation}
				\theta_n = \frac{\jmath X_n - Z^*}{\jmath X_n + Z} = \exp(\jmath \phi_n),
				\label{eq:reflection_coefficient_ris}
			\end{equation}
			where $X_n$ is the reactance and $\phi_n$ is the phase shift on the scattered wave.
			For a total of $N_\mathrm{S}$ elements, the \gls{ris} scattering matrix is \emph{diagonal with complex unit-magnitude entries}
			\begin{equation}
				\mathbf{\Theta} = \mathrm{diag}(\theta_1, \ldots, \theta_{N_\mathrm{S}}) =
				\begin{bmatrix}
					\theta_1 & 0 & \cdots & 0 \\
					0 & \theta_2 & \cdots & 0 \\
					\vdots & \vdots & \ddots & \vdots \\
					0 & 0 & \cdots & \theta_{N_\mathrm{S}}
				\end{bmatrix}.
			\end{equation}
			Despite the strong assumptions, this diagonal phase shift model is widely used for the analysis of \gls{ris} systems due to its simplicity and analytical tractability.
		\end{subsubsection}

@@

	\begin{subsection}{Applications}
		\begin{figure}[!t]
			\centering
			\subfloat[Monostatic backscatter]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/chapter_2/mbc.tex}
				}
				\label{fg:mbc}
			}
			\subfloat[Bistatic backscatter]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/chapter_2/bbc.tex}
				}
				\label{fg:bbc}
			}
			\\
			\subfloat[Ambient backscatter]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/chapter_2/ambc.tex}
				}
				\label{fg:ambc}
			}
			\subfloat[Symbiotic radio]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/chapter_2/sr.tex}
				}
				\label{fg:sr}
			}
			\caption{
				Illustration of scattering applications.
				The blue flows denote the primary link while the magenta flows denote the backscatter link.
			}
		\end{figure}

		\begin{subsubsection}{\glsfmtfull{mbc}}
			\gls{mbc} is the most common architecture where the carrier emitter and reader are integrated into one device called interrogator.
			As shown in \subref*{fg:backcom_monostatic} and \subref*{fg:mbc}, the interrogator transmits a \gls{cw} in the downlink and receives the reflected information-bearing signal in the uplink.
			The node varies its load impedance over time to switch between two states.
			Ideally, a full absorption (perfect matching, $\Gamma_0 = 0$) maps to bit ``0'' where energy is harvested, and a full reflection (perfect mismatch, $\lvert \Gamma_1 \rvert = 1$) maps to bit ``1'' where \gls{snr} is determined.
			\gls{mbc} is widely used in \gls{rfid} systems.
			The integrated transceiver design reduces the hardware cost but suffers from strong self-interference and limited coverage.
		\end{subsubsection}

		\begin{subsubsection}{\glsfmtfull{bbc}}
			\gls{bbc} separates the carrier emitter and reader into two individual devices, as illustrated in \subref*{fg:backcom_bistatic} and \subref*{fg:bbc}.
			This helps to combat self-interference and extend the operation range, but the system involves three devices and requires more complex coordination and synchronization.
			It is more popular in more complicated scenarios like \gls{wsn} and \gls{iot} with potentially moving nodes.
		\end{subsubsection}

		\begin{subsubsection}{\glsfmtfull{ambc}}
			\gls{ambc} has been recognized as a revolutionary technology since its debut in 2013 \cite{Liu2013b}.
			As shown in \subref*{fg:ambc}, it gets rid of dedicated \gls{rf} sources and relies on ambient signals (e.g., TV, FM, and Wi-Fi) for both energy harvesting and information transfer.
			Compared with \gls{mbc} and \gls{bbc}, its carrier waveform is no longer a \gls{cw} but a mixture of already modulated signals with different frequencies and amplitudes, which makes the detection more challenging.
			Therefore, it often employs \gls{fsk} modulation to shift the scattered signals to a different band for reduced interference on both coexisting systems.
			\gls{ambc} is a plug-and-play and environmental-friendly \gls{iot} solution, but its practical deployment is limited by the availability and quality of ambient signals.
		\end{subsubsection}

		\begin{subsubsection}{\glsfmtfull{sr}}
			\gls{sr} is a relatively new concept proposed in 2019 that introduced itself as ``cooperative \gls{ambc}'' \cite{Guo2019b}.
			As shown in \subref*{fg:sr}, it shares not only the transmitter, \gls{rf} source, but also the receiver with a primary transmission.
			This is different from traditional \gls{ambc} where the legacy system can be unaware of the backscatter link and the node wants to minimize its footprint.
			Such a symbiotic interaction can improve the reliability of the backscatter link as well as the energy efficiency of the primary link, but unavoidably challenges the system design.
			For example, the acquisition of backscatter \gls{csi} can be difficult due to its passive characteristic, the detection of node message may involve complicated signal processing like \gls{sic}, and the synchronization of both links can be nontrivial due to the load-switching constraints.
			If those issues can be mitigated, \gls{sr} would be a win-win solution that supercharges resource-constrained devices by leveraging the existing network infrastructure.
		\end{subsubsection}
	\end{subsection}
\end{section}

>>>>

		\begin{subsubsection}{Diagonal Phase Shift Model}
			A straightforward way to model the \gls{ris} scattering effect is to consider independent scattering elements with purely reactive load impedance \cite{Wu2018}.
			The reflection coefficient of the $n$-th element is thus
			\begin{equation}
				\theta_n = \frac{\jmath X_n - Z^*}{\jmath X_n + Z} = \exp(\jmath \phi_n),
				\label{eq:reflection_coefficient_ris}
			\end{equation}
			where $X_n$ is the reactance and $\phi_n$ is the phase shift on the scattered wave.
			For a total of $N_\mathrm{S}$ elements, the \gls{ris} scattering matrix is \emph{diagonal with complex unit-magnitude entries}
			\begin{equation}
				\mathbf{\Theta} = \mathrm{diag}(\theta_1, \ldots, \theta_{N_\mathrm{S}}) =
				\begin{bmatrix}
					\theta_1 & 0 & \cdots & 0 \\
					0 & \theta_2 & \cdots & 0 \\
					\vdots & \vdots & \ddots & \vdots \\
					0 & 0 & \cdots & \theta_{N_\mathrm{S}}
				\end{bmatrix}.
				\label{eq:diagonal_scattering_matrix}
			\end{equation}
			Despite the strong assumptions, this diagonal phase shift model is widely used for the analysis of \gls{ris} systems due to its simplicity and analytical tractability.
		\end{subsubsection}

@@

	\begin{subsection}{Applications}
		\begin{figure}[H]
			\centering
			\subfloat[Monostatic backscatter]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/chapter_2/mbc.tex}
				}
				\label{fg:mbc_intro}
			}
			\subfloat[Bistatic backscatter]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/chapter_2/bbc.tex}
				}
				\label{fg:bbc_intro}
			}
			\\
			\subfloat[Ambient backscatter]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/chapter_2/ambc.tex}
				}
				\label{fg:ambc_intro}
			}
			\subfloat[Symbiotic radio]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/chapter_2/sr.tex}
				}
				\label{fg:sr_intro}
			}
			\caption{
				Illustration of scattering applications.
				The blue flows denote the primary link while the magenta flows denote the backscatter link.
			}
		\end{figure}

		\begin{subsubsection}{\glsfmtfull{mbc}}
			\gls{mbc} is the most common architecture where the carrier emitter and reader are integrated into one device called interrogator.
			As shown in \subref*{fg:backcom_monostatic} and \subref*{fg:mbc_intro}, the interrogator transmits a \gls{cw} in the downlink and receives the reflected information-bearing signal in the uplink.
			The node varies its load impedance over time to switch between two states.
			Ideally, a full absorption (perfect matching, $\Gamma_0 = 0$) maps to bit ``0'' where energy is harvested, and a full reflection (perfect mismatch, $\lvert \Gamma_1 \rvert = 1$) maps to bit ``1'' where \gls{snr} is determined.
			\gls{mbc} is widely used in \gls{rfid} systems.
			The integrated transceiver design reduces the hardware cost but suffers from strong self-interference and limited coverage.
		\end{subsubsection}

		\begin{subsubsection}{\glsfmtfull{bbc}}
			\gls{bbc} separates the carrier emitter and reader into two individual devices, as illustrated in \subref*{fg:backcom_bistatic} and \subref*{fg:bbc_intro}.
			This helps to combat self-interference and extend the operation range, but the system involves three devices and requires more complex coordination and synchronization.
			It is more popular in more complicated scenarios like \gls{wsn} and \gls{iot} with potentially moving nodes.
		\end{subsubsection}

		\begin{subsubsection}{\glsfmtfull{ambc}}
			\gls{ambc} has been recognized as a revolutionary technology since its debut in 2013 \cite{Liu2013b}.
			As shown in \subref*{fg:ambc_intro}, it gets rid of dedicated \gls{rf} sources and relies on ambient signals (e.g., TV, FM, and Wi-Fi) for both energy harvesting and information transfer.
			Compared with \gls{mbc} and \gls{bbc}, its carrier waveform is no longer a \gls{cw} but a mixture of already modulated signals with different frequencies and amplitudes, which makes the detection more challenging.
			Therefore, it often employs \gls{fsk} modulation to shift the scattered signals to a different band for reduced interference on both coexisting systems.
			\gls{ambc} is a plug-and-play and environmental-friendly \gls{iot} solution, but its practical deployment is limited by the availability and quality of ambient signals.
		\end{subsubsection}

		\begin{subsubsection}{\glsfmtfull{sr}}
			\gls{sr} is a relatively new concept proposed in 2019 that introduced itself as ``cooperative \gls{ambc}'' \cite{Guo2019b}.
			As shown in \subref*{fg:sr_intro}, it shares not only the transmitter, \gls{rf} source, but also the receiver with a primary transmission.
			This is different from traditional \gls{ambc} where the legacy system can be unaware of the backscatter link and the node wants to minimize its footprint.
			Such a symbiotic interaction can improve the reliability of the backscatter link as well as the energy efficiency of the primary link, but unavoidably challenges the system design.
			For example, the acquisition of backscatter \gls{csi} can be difficult due to its passive characteristic, the detection of node message may involve complicated signal processing like \gls{sic}, and the synchronization of both links can be nontrivial due to the load-switching constraints.
			If those issues can be mitigated, \gls{sr} would be a win-win solution that supercharges resource-constrained devices by leveraging the existing network infrastructure.
		\end{subsubsection}
	\end{subsection}
\end{section}

### 2024-03-27 content/chapter_3.tex
:pencil: Update chapter 4

		\emph{First,} we propose a novel \gls{ris}-aided \gls{swipt} architecture based on joint waveform, active and passive beamforming design under the diode nonlinear model \eqref{eq:dc_power_nonlinear} \cite{Clerckx2016a}. Although this tractable harvester model accurately reveals how the input power level and waveform shape influence the output \gls{dc} power, it also introduces design challenges such as frequency coupling (i.e., components of different frequencies compensate and produce \gls{dc}), waveform coupling (i.e., different waveforms jointly contribute to \gls{dc}), and high-order objective function. To make an efficient use of the rectifier nonlinearity, we superpose a multi-carrier unmodulated power waveform (deterministic multisine) to a multi-carrier modulated information waveform and evaluate the performance under the \gls{ts} and \gls{ps} receiving modes. The proposed joint waveform, active and passive beamforming architecture exploits the rectifier nonlinearity, the channel selectivity, and a beamforming gain across frequency and spatial domains to enlarge the achievable \gls{r-e} region. This is the first work to propose a joint waveform, active and passive beamforming architecture for \gls{ris}-aided \gls{swipt}.

		\emph{Second,} we characterize each \gls{r-e} boundary point by energy maximization under a rate constraint. The problem is solved by a \gls{bcd} algorithm based on the \gls{csit}. For active beamforming, we prove that the global optimal active information and power precoders coincide at \gls{mrt} even with rectifier nonlinearity. For passive beamforming, we propose a \gls{sca} algorithm and retrieve the \gls{ris} phase shift by eigen decomposition with optimality proof. Finally, the superposed waveform and the splitting ratio are optimized by the \gls{gp} technique. The \gls{ris} phase shift, active precoder, and waveform amplitude are updated iteratively until convergence. This is the first work to jointly optimize waveform and active/passive beamforming in \gls{ris}-aided \gls{swipt}.

		\emph{Third,} we introduce two closed-form adaptive waveform schemes to avoid the exponential complexity of the \gls{gp} algorithm. To facilitate practical \gls{swipt} implementation, the \gls{wf} strategy for modulated waveform and the \gls{smf} strategy for multisine waveform are combined in time and power domains, respectively. The passive beamforming design is also adapted to accommodate the low-complexity waveform schemes. The proposed low-complexity \gls{bcd} algorithm achieves a good balance between performance and complexity.

		\emph{Fourth,} we provide numerical results to evaluate the proposed algorithms. It is concluded that:
		\begin{itemize}
			\item \gls{ris} enables constructive reflection and flexible subchannel design in the frequency domain that is essential for \gls{swipt} systems;
			\item \gls{ris} mainly affects the effective channel instead of the waveform design;
			\item Multisine waveform is beneficial to energy transfer especially when the number of subbands is large;
			\item \gls{ts} is preferred at low \gls{snr} while \gls{ps} is preferred at high \gls{snr};
			\item There exist two optimal \gls{ris} development locations, one close to the \gls{ap} and one close to the \gls{ue};
			\item The output \gls{snr} scales linearly with the number of transmit antennas and quadratically with the number of \gls{ris} elements;
			\item Due to the rectifier nonlinearity, the output \gls{dc} scales quadratically with the number of transmit antennas and quartically with the number of \gls{ris} elements;
			\item For narrowband \gls{swipt}, the optimal active and passive beamforming for any \gls{r-e} point are also optimal for the whole \gls{r-e} region;
			\item For broadband \gls{swipt}, the optimal active and passive beamforming depend on specific \gls{r-e} point and require adaptive designs;
			\item The proposed algorithms are robust to practical impairments such as inaccurate cascaded \gls{csit} and finite \gls{ris} reflection states.
		\end{itemize}
	\end{subsection}
\end{section}

\begin{section}{System Model}\label{sc:system_model}
	\begin{figure}[H]
		\centering
		\def\svgwidth{0.9\columnwidth}
		\input{assets/chapter_3/system.eps_tex}
		\caption{An \gls{ris}-aided multi-carrier \gls{miso} \gls{swipt} system.}
		\label{fg:system}
	\end{figure}

@@

		\begin{subsubsection}{Imperfect \gls{csit}}
			\begin{figure}[H]
				\centering
				\subfloat[Imperfect cascaded \gls{csit}\label{fg:re_csi}]{
					\resizebox{0.45\columnwidth}{!}{
						% \includegraphics{assets/re_csi.eps}
						\input{assets/chapter_3/re_csi.tex}
					}
				}
				\subfloat[Quantized \gls{ris}\label{fg:re_quantization}]{
					\resizebox{0.45\columnwidth}{!}{
						% \includegraphics{assets/re_quantization.eps}
						\input{assets/chapter_3/re_quantization.tex}
					}
				}
				\caption{Average \gls{r-e} region with imperfect cascaded \gls{csit} and quantized \gls{ris} for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\qty{-40}{dBm}$, $B=\qty{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\qty{2}{\meter}$. $\epsilon_{n}=0$ and $\epsilon_{n}=\infty$ correspond respectively to perfect \gls{csit} and no \gls{csit} (and random \gls{ris}); $b=0$ and $b \to \infty$ correspond respectively to no \gls{ris} and continuous \gls{ris}.}
			\end{figure}

>>>>

		First, we propose a novel \gls{ris}-aided \gls{swipt} architecture based on joint waveform, active and passive beamforming design under the diode nonlinear model \eqref{eq:dc_power_nonlinear} \cite{Clerckx2016a}. Although this tractable harvester model accurately reveals how the input power level and waveform shape influence the output \gls{dc} power, it also introduces design challenges such as frequency coupling (i.e., components of different frequencies compensate and produce \gls{dc}), waveform coupling (i.e., different waveforms jointly contribute to \gls{dc}), and high-order objective function. To make an efficient use of the rectifier nonlinearity, we superpose a multi-carrier unmodulated power waveform (deterministic multisine) to a multi-carrier modulated information waveform and evaluate the performance under the \gls{ts} and \gls{ps} receiving modes. The proposed joint waveform, active and passive beamforming architecture exploits the rectifier nonlinearity, the channel selectivity, and a beamforming gain across frequency and spatial domains to enlarge the achievable \gls{r-e} region. This is the first work to propose a joint waveform, active and passive beamforming architecture for \gls{ris}-aided \gls{swipt}.

		Second, we characterize each \gls{r-e} boundary point by energy maximization under a rate constraint. The problem is solved by a \gls{bcd} algorithm based on the \gls{csit}. For active beamforming, we prove that the global optimal active information and power precoders coincide at \gls{mrt} even with rectifier nonlinearity. For passive beamforming, we propose a \gls{sca} algorithm and retrieve the \gls{ris} phase shift by eigen decomposition with optimality proof. Finally, the superposed waveform and the splitting ratio are optimized by the \gls{gp} technique. The \gls{ris} phase shift, active precoder, and waveform amplitude are updated iteratively until convergence. This is the first work to jointly optimize waveform and active/passive beamforming in \gls{ris}-aided \gls{swipt}.

		Third, we introduce two closed-form adaptive waveform schemes to avoid the exponential complexity of the \gls{gp} algorithm. To facilitate practical \gls{swipt} implementation, the \gls{wf} strategy for modulated waveform and the \gls{smf} strategy for multisine waveform are combined in time and power domains, respectively. The passive beamforming design is also adapted to accommodate the low-complexity waveform schemes. The proposed low-complexity \gls{bcd} algorithm achieves a good balance between performance and complexity.

		Fourth, we provide numerical results to evaluate the proposed algorithms. It is concluded that:
		\begin{itemize}
			\item \gls{ris} enables constructive reflection and flexible subchannel design in the frequency domain that is essential for \gls{swipt} systems;
			\item \gls{ris} mainly affects the effective channel instead of the waveform design;
			\item Multisine waveform is beneficial to energy transfer especially when the number of subbands is large;
			\item \gls{ts} is preferred at low \gls{snr} while \gls{ps} is preferred at high \gls{snr};
			\item There exist two optimal \gls{ris} development locations, one close to the \gls{ap} and one close to the \gls{ue};
			\item The output \gls{snr} scales linearly with the number of transmit antennas and quadratically with the number of \gls{ris} elements;
			\item Due to the rectifier nonlinearity, the output \gls{dc} scales quadratically with the number of transmit antennas and quartically with the number of \gls{ris} elements;
			\item For narrowband \gls{swipt}, the optimal active and passive beamforming for any \gls{r-e} point are also optimal for the whole \gls{r-e} region;
			\item For broadband \gls{swipt}, the optimal active and passive beamforming depend on specific \gls{r-e} point and require adaptive designs;
			\item The proposed algorithms are robust to practical impairments such as inaccurate cascaded \gls{csit} and finite \gls{ris} reflection states.
		\end{itemize}
	\end{subsection}
\end{section}

\begin{section}{System Model}
	\begin{figure}[H]
		\centering
		\def\svgwidth{0.9\columnwidth}
		\input{assets/chapter_3/system.eps_tex}
		\caption{An \gls{ris}-aided multi-carrier \gls{miso} \gls{swipt} system.}
		\label{fg:system}
	\end{figure}

@@

		\begin{subsubsection}{Imperfect \glsfmtshort{csit}}
			\begin{figure}[H]
				\centering
				\subfloat[Imperfect cascaded \gls{csit}\label{fg:re_csi}]{
					\resizebox{0.45\columnwidth}{!}{
						% \includegraphics{assets/re_csi.eps}
						\input{assets/chapter_3/re_csi.tex}
					}
				}
				\subfloat[Quantized \gls{ris}\label{fg:re_quantization}]{
					\resizebox{0.45\columnwidth}{!}{
						% \includegraphics{assets/re_quantization.eps}
						\input{assets/chapter_3/re_quantization.tex}
					}
				}
				\caption{Average \gls{r-e} region with imperfect cascaded \gls{csit} and quantized \gls{ris} for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\qty{-40}{dBm}$, $B=\qty{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\qty{2}{\meter}$. $\epsilon_{n}=0$ and $\epsilon_{n}=\infty$ correspond respectively to perfect \gls{csit} and no \gls{csit} (and random \gls{ris}); $b=0$ and $b \to \infty$ correspond respectively to no \gls{ris} and continuous \gls{ris}.}
			\end{figure}
